Defending Against Web Application Attacks: Approaches, Challenges and Implications \vspace{-1mm}

### 2016-07-25 docs/comments/comments.tex
addressed comment 3 of R1
addressed R1's comment 1, also the updated text in the paper is now in yellow color

@@

\noindent
{\bf Comment 3:} ``Some minor comments for the authors:
\begin{itemize}
\item Introduction ``didn't" $\rightarrow$ did not
\item Introduction ``haven't" $\rightarrow$ have not
\item Section 2: PHP Object Injection vulnerabilities do not have to be
 ``part of cookies". These could come any user input, not necessarily
 cookies (similar to other code injection vulnerabilities).
\item Section 4.5 ``canny attacks" and ``cannier attacker" should probably
 be ``savvy" or a different word.
\item Section 5.1.2 it is not clear from your description that the CSP
 policy is communicated via HTTP header. This may not be clear to
 those readers that aren't familiar with CSP.
\item Section 5.1.2 ``XXS" $\rightarrow$ ``XSS".
\item Section 5.2.1 ``maybe" $\rightarrow$ ``may be"".
\end{itemize}

>>>>

\noindent
{\bf Response:}
Indeed,
an application firewall is actually a defense
mechanism that fits in our study.
Besides,
in reference~\cite{DPJV06}
the authors indicate three mechanisms~\cite{BK04,PB05,HO05b}
that we include in our study as
application firewalls.
Such mechanisms though,
can be seen as host-based application firewalls
which are different from the network-based
application firewalls.
Mechanisms coming from the later category
operate directly at the application
layer of the protocol stack and
in most cases they are modules
of the web server
(e.g. {\tt modsecurity})\footnote{\url{https://www.modsecurity.org/}}.
Even though we do not include such mechanisms
(note also that {\tt modsecurity} is
not a research approach),
they can be analyzed based on our criteria.\\
% note: I do not know if we must update the text
% of the paper to address the above comment.

@@

\noindent
{\bf Comment 3:} ``Some minor comments for the authors:
\begin{enumerate}
\item Introduction: ``didn't" $\rightarrow$ did not
\item Introduction: ``haven't" $\rightarrow$ have not
\item Section 2: PHP Object Injection vulnerabilities do not have to be
 ``part of cookies". These could come any user input, not necessarily
 cookies (similar to other code injection vulnerabilities).
\item Section 4.5 ``canny attacks" and ``cannier attacker" should probably
 be ``savvy" or a different word.
\item Section 5.1.2 it is not clear from your description that the CSP
 policy is communicated via HTTP header. This may not be clear to
 those readers that aren't familiar with CSP.
\item Section 5.1.2 ``XXS" $\rightarrow$ ``XSS".
\item Section 5.2.1 ``maybe" $\rightarrow$ ``may be"".
\end{enumerate}

\noindent
{\bf Response:}
We have updated the text accordingly.\\

### 2016-07-25 docs/paper/questioning.tex
addressed R1's comment 1, also the updated text in the paper is now in yellow color

@@

Then, we {\it categorize} a selection of representative
protection mechanisms. In our selection we include protection
mechanisms that counter web attacks when they take place,
while we do not consider countermeasures that identify
vulnerabilities using static program analysis~\cite{SZ12}
(which takes place during the development or testing
phases). Similarly, dynamic analysis techniques that examine
applications to identify vulnerabilities that may lead to the attacks
that we described earlier are out of scope as well. Note also, that we
didn't consider mechanisms that haven't been presented in research papers.

@@

A recent attack called {\sc php} Object Injection
({\sc poi})~\cite{DKH14} does not directly involve
the injection of code, but still achieves arbitrary code execution
in the context of a {\sc php} application through the
injection of specially crafted objects.
These objects are injected as part of cookies,
which, when deserialized
by the application, result in arbitrary code execution.
Note that the exploitation model we propose
in the following Section also captures such attacks.

@@

Defenders and attackers are often caught in a cat-and-mouse game,
where countermeasures are bypassed by canny attacks, which are caught
by more sophisticated countermeasures, yet again bypassed by cannier
attacks, and so on. We use security to refer to the ability of a
detection mechanism to resist circumvention.

@@

A policy enforcement technique developed by Mozilla,
called {\sc csp} (Content Security
Policy)\footnote{\scriptsize\url{https://developer.mozilla.org/en-US/docs/Web/Security/CSP}}~\cite{SSM10}
is currently supported by many browsers to prevent
{\sc xss} and {\sc csrf} attacks. To eliminate such
attacks, web site administrators
can specify which domains the browser should treat
as valid sources of script and which not. Then, the browser
(Point {\sc ub}) will only execute scripts that exist in
source files from white-listed domains.
Note that,
if an application involves
embedded scripts, developers must utilize
the {\sc csp}'s {\em nonce} concept.
This is an unpredictable,
random value indicated in
the {\tt script-src} directive which in turn,
is applied as a nonce attribute to
{\tt <script>} elements.
As a result, only those elements that have the
correct nonce will execute.
Even if an attacker
is able to inject markup into the page,
the attack will be prevented by the attacker's
inability to guess the nonce value.
However, attackers may still bypass this feature
and invoke a script from a non-whitelisted source.
To do so, their injected code must
be crafted in a way that the nonce is handled
by the browser as an attribute of the payload~\cite{jigsaw}.
\vspace{-0.5mm}

Another policy enforcement approach introduces
policies directly either in {\sc html} or JavaScript code
to confine their behavior. BrowserShield~\cite{RDWDE07}
acts as a proxy on the server-side (Point {\sc s}t{\sc b}) to
parse the {\sc html} of server responses and identify
scripts. Then, it rewrites them into safe equivalents
and protects the web user from exploits
that are based on reported browser vulnerabilities.
ConScript~\cite{ML10}, CoreScript~\cite{YCIS07},
and the framework by Phung et al.~\cite{PSC09}
extend JavaScript with new primitive functions that
provide safe methods to protect potentially vulnerable
JavaScript functions. In both cases, policy enforcement takes
place at client-side, in the JavaScript engine of the browser (Point {\sc ub}).
In this way, {\sc xxs} attacks that take advantage
of functions such as {\tt write} and {\tt eval}, which are
used to assemble innocuous-looking parts into harmful
strings,\footnote{\scriptsize The infamous Sammy worm that
infected MySpace in 2005~\cite{ELX07}
utilized the {\tt eval} function to assemble a
malicious script.} would fail.

@@

An issue that involves all taint tracking schemes involves
the difficulty of maintaining accurate taints~\cite{GMPS11}
(e.g. implicit flows~\cite{ME07}).
In such cases, certain, tainted inputs can escape the tracking mechanism.
Keeping track of such input maybe impractical not only because of the
various technical difficulties, but also because it would raise false alarms.

>>>>

\usepackage{fixltx2e}
\usepackage{soul,color}
\usepackage[dvipsnames]{xcolor}

\newcommand{\hlc}[2][yellow]{ {\sethlcolor{#1} \hl{#2}} }

@@

Then, we {\it categorize} a selection of representative
protection mechanisms. In our selection we include protection
mechanisms that counter web attacks when they take place,
while we do not consider countermeasures that identify
vulnerabilities using static program analysis~\cite{SZ12}
(which takes place during the development or testing
phases). Similarly, dynamic analysis techniques that examine
applications to identify vulnerabilities that may lead to the attacks
that we described earlier are out of scope as well. Note also, that we
\hlc[yellow]{did not} consider mechanisms that
\hlc[yellow]{have not} been presented in research papers.

@@

\hlc[yellow]{A recent attack called {\sc php} Object Injection
({\sc poi})}~\cite{DKH14} \hlc[yellow]{does not directly involve
the injection of code, but still achieves arbitrary code execution
in the context of a {\sc php} application through the
injection of specially crafted objects
(e.g. as part of cookies).
When deserialized
by the application, these objects result in
arbitrary code execution.}
Note that the exploitation model we propose
in the following Section also captures such attacks.

@@

Defenders and attackers are often caught in a cat-and-mouse game,
where countermeasures are bypassed by \hlc[yellow]{savvy} attacks, which are caught
by more sophisticated countermeasures, yet again bypassed by \hlc[yellow]{savvier}
attacks, and so on. We use security to refer to the ability of a
detection mechanism to resist circumvention.

@@

A policy enforcement technique developed by Mozilla,
called {\sc csp} (Content Security
Policy)\footnote{\scriptsize\url{https://developer.mozilla.org/en-US/docs/Web/Security/CSP}}~\cite{SSM10}
is currently supported by many browsers to prevent
{\sc xss} and {\sc csrf} attacks. To eliminate such
attacks, web site administrators
can specify which domains the browser should treat
as valid sources of script and which not.
\hlc[yellow]{These policies are communicated via the {\sc http} header.}
Then, the browser
(Point {\sc ub}) will only execute scripts that exist in
source files from white-listed domains.
Note that,
if an application involves
embedded scripts, developers must utilize
the {\sc csp}'s {\em nonce} concept.
This is an unpredictable,
random value indicated in
the {\tt script-src} directive which in turn,
is applied as a nonce attribute to
{\tt <script>} elements.
As a result, only those elements that have the
correct nonce will execute.
Even if an attacker
is able to inject markup into the page,
the attack will be prevented by the attacker's
inability to guess the nonce value.
However, attackers may still bypass this feature
and invoke a script from a non-whitelisted source.
To do so, their injected code must
be crafted in a way that the nonce is handled
by the browser as an attribute of the payload~\cite{jigsaw}.
\vspace{-0.5mm}

Another policy enforcement approach introduces
policies directly either in {\sc html} or JavaScript code
to confine their behavior. BrowserShield~\cite{RDWDE07}
acts as a proxy on the server-side (Point {\sc s}t{\sc b}) to
parse the {\sc html} of server responses and identify
scripts. Then, it rewrites them into safe equivalents
and protects the web user from exploits
that are based on reported browser vulnerabilities.
ConScript~\cite{ML10}, CoreScript~\cite{YCIS07},
and the framework by Phung et al.~\cite{PSC09}
extend JavaScript with new primitive functions that
provide safe methods to protect potentially vulnerable
JavaScript functions. In both cases, policy enforcement takes
place at client-side, in the JavaScript engine of the browser (Point {\sc ub}).
In this way, \hlc[yellow]{{\sc xss}} attacks that take advantage
of functions such as {\tt write} and {\tt eval}, which are
used to assemble innocuous-looking parts into harmful
strings,\footnote{\scriptsize The infamous Sammy worm that
infected MySpace in 2005~\cite{ELX07}
utilized the {\tt eval} function to assemble a
malicious script.} would fail.

@@

An issue that involves all taint tracking schemes involves
the difficulty of maintaining accurate taints~\cite{GMPS11}
(e.g. implicit flows~\cite{ME07}).
In such cases, certain, tainted inputs can escape the tracking mechanism.
Keeping track of such input \hlc[yellow]{may be} impractical not only because of the
various technical difficulties, but also because it would raise false alarms.
